Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

```{r fig.height=3.5*5, fig.width=10*5, dpi=300}
plot_distribution2 <- function(data_rataan, title, color) {
  df_rataan <- data.frame(x = data_rataan)

@@

>>>>

```{r fig.height=3.5*4, fig.width=6*4, dpi=300}
plot_distribution2 <- function(data_rataan, title, color) {
  df_rataan <- data.frame(x = data_rataan)

@@

histo <- function(dist, title, color) {
  df <- data.frame(x = c(dist))

  # Histogram rataan sampel
  p1 <- ggplot(data = df, aes(x = x)) +
    geom_histogram(bins = 20, fill = color, color="black", alpha = 1, aes(y = ..density..)) +
    geom_density(fill = color, adjust = 3, size = 1, alpha=.5) +
    labs(title = paste0("Sebaran Populasi ", title)) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 10, face = "bold", hjust = 0.5)
    )

  return(p1)
}

all_plots <- c(
  histo(norm_data, paste0("Normal"), color="#357a87"),
  histo(mix_data_1, paste0("Campuran 1"), color="#792b9a"),
  histo(mix_data_2, paste0("Campuran 2"), color="#96336c"),
  histo(mix_data_3, paste0("Campuran 3"), color="#9a3b1a")
)

# Menentukan tinggi relatif dari setiap baris
rel_heights <- c(rep(2/8, 4), rep(1/8, 7))
plot_grid(plotlist = all_plots, ncol = 8, rel_heights = rel_heights)
```

```{r fig.height=3.5*4, fig.width=6*4, dpi=300}
plot_distribution2 <- function(data_rataan, title, color) {
  df_rataan <- data.frame(x = data_rataan)

histo <- function(dist, title, color){
  df <- data.frame(x = dist)

  # Histogram rataan sampel
  p1 <- ggplot(data = df, aes(x = x)) +
    geom_histogram(bins = 20, fill = color, color="black",alpha = 1, aes(y = ..density..)) +
    geom_density(fill = color, adjust = 3, size = 1, alpha=.5) +
    labs(title = paste0("Sebaran Populasi ", title)) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 10, face = "bold", hjust = 0.5)
    )
  hist(norm_data, main = "Sebaran Populasi Campuran 1", 
       xlab = "Nilai", ylab = "Frekuensi", col = "#357a87") 
}

all_plots <- c(
  histo(norm_data, paste0("Normal"), color="#357a87"),
  histo(mix_data_1, paste0("Campuran 1"), color="#792b9a"),
  histo(mix_data_2, paste0("Campuran 2"), color="#96336c"),
  histo(mix_data_3, paste0("Campuran 3"), color="#9a3b1a")  
)
